---
title: "OMDB API Movie Fetcher"
author: "Jiahao Yuan, Yunfan Wu"
date: "2025-03-17"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{OMDB API Movie Fetcher}
  %\VignetteEngine{rmarkdown::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# OMDB API Movie Fetcher

This package allows you to interact with the OMDB API to fetch movie details based on some movie information. It provides functions to fetch accurate movie information using either a movie title or IMDB ID, or perform rough searches by partial title, and handle movie data in batches.

```{r}
library(OMDB.API)
```


## Functions

### `set.omdb.api.key()`

This function allows you to set your OMDB API key, which is required for making requests to the OMDB API. The API key will be stored in package environment.

#### Parameters:

- `api_key`: Your OMDB API key string (e.g., `"22bda3a2"`).

#### Example:

```{r}
set.omdb.api.key("22bda3a2")
```


### `unset.omdb.api.key()`

This function removes the OMDB API key from the environment, so that you can use set a new API key to the package environment.

#### Example:

```{r}
unset.omdb.api.key()
```


### `get.accurate.omdb.info()`

This function fetches detailed information for a movie, either by **IMDb ID** or **title**.

#### Parameters:

- `id`: The IMDb ID of the movie (e.g., `"tt1285016"`).
- `title`: The title of the movie (e.g., `"Avengers"`).
- `type`: The type of result, which can be `"movie"`, `"series"`, or `"episode"`.
- `year`: The release year of the movie.
- `plot`: The length of the plot to return (`"short"` or `"full"`).

#### Example:

```{r}
# Set your OMDB API key
set.omdb.api.key("22bda3a2")

# Fetch movie info by title
movie_info_1 <- get.accurate.omdb.info(title = "Avengers")
print(movie_info_1)

# Fetch movie info by IMDb ID
movie_info_2 <- get.accurate.omdb.info(id = "tt1285016")
print(movie_info_2)
```


### `get.batch.accurate.omdb.info()`

This function allows you to fetch information for a **batch** of movies, given a list of IMDb IDs.

#### Parameters

- `ids`: A vector of IMDb IDs (e.g., `c("tt1285016", "tt1285017")`).

#### Example

```{r}
# Fetch information for multiple movies
movie_ids <- c("tt1285016", "tt1285017")
batch_info <- get.batch.accurate.omdb.info(ids = movie_ids)
print(batch_info)
```


### `get.rough.omdb.info()`

This function performs a rough search for movies based on a **partial title**, with optional filters like **minimum rating**, **genre**, and **sort order**.

#### Parameters

- `title`: The partial title of the movie (e.g., `"Avengers"`).
- `type`: The type of result, which can be `"movie"`, `"series"`, or `"episode"`.
- `year`: The release year of the movie to filter the results.
- `min_rating`: The minimum rating for the movie (e.g., 7).
- `genre`: The genre of the movie (e.g., `"Action"`).
- `sort_order`: The order in which the results are sorted (`"asc"`, `"desc"`, or `"none"`).

#### Example

```{r}
# Rough search for movies with title "Avengers" and minimum rating of 7
rough_results <- get.rough.omdb.info(title = "Avengers", min_rating = 7, genre = "Action")
print(rough_results)

# Sort the results by IMDb rating in descending order
sorted_results <- get.rough.omdb.info(title = "Avengers", min_rating = 7, sort_order = "desc")
print(sorted_results)
```

## Usage Overview

To use the functions in this package, please follow these steps:

1. Set your OMDB API key using the `set.omdb.api.key()` function. After setting the OMDB API key, you can choose **Steps 2, 3, 4** freely to get your target movie information.

2. Use `get.accurate.omdb.info()` to fetch detailed movie information by IMDb ID or title.

3. Use `get.batch.accurate.omdb.info()` to fetch information for a batch of movies.

4. Use `get.rough.omdb.info()` for rough searches based on a partial title with additional filters (e.g., rating, genre).

5. After finishing, you can remove your API key using `unset.omdb.api.key()`.
